The K2 Halo Photometry Campaign

### 2019-03-11 paper/ms.tex
comments and short cadence and stuff

% short cadence availability

@@

Some of the objects here have been previously published, but we here provide the first public data releases for the Pleiades' Seven Sisters \citep{White2017}, Aldebaran \citep{Farr2018}, $\iota$~Lib \citep{Buysschaert2018}, and $\epsilon$~Tau \citep{arentoft2019}.

@@

% do k2 smear after that

>>>>

% short cadence availability 
Seven stars in Campaign~13 and one in Campaign~16 were not only assigned long-cadence halo apertures, but also downloaded at short cadence. TV-min halo photometry appears to perform poorly on short-cadence data, however, and we do not consider the data products for these stars to be satisfactory for an initial data release. This may be to do with the total variation being a poor proxy for noise in the light curves, with relatively fewer thruster-firing jumps and relatively higher white noise. The long-cadence data appear to be of normal quality.

@@

Some of the objects here have been previously published, but we here provide the first public data releases for the Pleiades' Seven Sisters \citep{White2017}, Aldebaran \citep{Farr2018}, $\iota$~Lib \citep{Buysschaert2018}, and $\epsilon$~Tau \citep{Arentoft2019}, as well as $\rho$~Leo with halo photometry but without using the TV-min method \citep{Aerts2018}.

@@

% do k2 smear after that
The sample of K2 bright stars presented here only includes those with halo apertures, but while some others are available conventionally, many were not assigned target pixels and were not downloaded at all. Light curves for many of these stars can nevertheless be obtained with smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD. These can be used to recover the 102 brightest otherwise-unobserved stars in nominal \kepler (Pope et al., in prep.), and also in K2, although in the latter case the sample is much smaller due to competition with halo apertures and the systematics correction is more difficult. A natural extension of both pieces of work would be to produce smear light curves of all bright stars without halo apertures in K2, which would finally make the \kepler extended mission magnitude-complete at the bright end.
